### 2020-02-22 doc/icfp20/music.tex
improve music section

\paragraph{Pitches}
In music, a \emph{pitch} is a value denoting how high or low a sound is.
Pitches can be represented either as an absolute value or as a relative
value paired with the octave the sound belongs to.
In our implementation, the two representations of pitches are defined
as the \texttt{Pitch} and \texttt{PitchOctave} datatypes, respectively,
accompanied by a proof that converting back and forth between them
is an identity.

@@

\paragraph{Duration}
\emph{Duration} denotes a certain unit of time during which a sound
or silence lasts.
The unit is unspecified at the composition time; it is instantiated to
a concrete value when the music is played at a specific tempo.

@@

\emph{Intervals} are yet another key concept in music.
An interval denotes the difference in pitch between two notes.
There are 13 kinds of interval within an octave, and these intervals
may be classified from several different perspectives: (i) major or minor;
(ii) consonant or dissonant; and (iii) perfect or imperfect.
As a convention, we refer to \texttt{min2} and \texttt{maj2}  uniformly
as ``2nd'', and similarly for other intervals.
We also call \texttt{per1} the \emph{unison} in the rest of this section.

>>>>

\paragraph{Pitches}
A \emph{pitch} is a value denoting how high or low a sound is.
In our implementation, pitches have type \texttt{Pitch} and take the
form \texttt{name octave}, where \texttt{name} is a name ranging
over \texttt{c}, \texttt{d}, \texttt{e}, etc. and \texttt{octave} is a
natural number denoting which octave the pitch belongs to.
For instance, the middle C is represented as \texttt{c 5}.

@@

\paragraph{Duration}
\emph{Duration} denotes an unspecified unit of time during which a
sound or silence lasts.
In our implementation, duration (of type \texttt{Duration} is simply
a natural number, denoting the relative length within a bar (such as
whole and half).
When the music is played at a specific tempo, the number is 
multiplied by a velocity and turned into an absolute length.

@@

\emph{Intervals} are a concept denoting the difference in pitch
between two notes.
There are 13 kinds of interval within an octave, and these intervals
can be classified from several different perspectives: (i) major or
minor; (ii) consonant or dissonant; and (iii) perfect or imperfect.
We define intervals as a datatype \texttt{Interval}, where each
constructor represents one of the 13 intervals.
